---
title: "Plot Test: Google Vis"
author: "John Yuill"
date: "December 11, 2016"
output: html_document
---

## PURPOSE
* test out Google Vis package

## EXAMPLES


## Google Viz

```{r setOptions, message=FALSE}
library(googleVis)
op <- options(gvis.plot.tag='chart')
```

```{r scatterexample, results='asis', tidy=FALSE, echo=FALSE, message=FALSE}

mtdm2 <- mtcars[,c(1,3)]
scatter <- gvisScatterChart(mtdm2,
                            options=list(
                              pointSize=2,
                              width=400,
                              height=400,
                              legend="none"
                   
                 )
                 )
#plot(scatter)
#scatter
print(scatter, 'chart')

```

#### Pros
* Well-developed Google chart library

#### Cons
* displays in browser, not R plot window
* doesn't directly integrate with R Markdown HTML docs - fidgetly to get it to work

## Conclusion

* ggplot for exploration within R and for static charts in R markdown
* get up to speed with more ggvis, as it is likely future of R graphics
* get up to speed on shiny + ggvis
* keep plotly in mind for situations that may arise
