---
title: "Plot Test: Google Vis"
author: "John Yuill"
date: "December 11, 2016"
output: html_document
---

## PURPOSE
* test out Google Vis package

## EXAMPLES


## Google Viz

```{r setOptions, message=FALSE}
library(googleVis)
op <- options(gvis.plot.tag='chart')
```


```{r ComboExample, results='asis', tidy=TRUE}
## Add the mean
CityPopularity$Mean=mean(CityPopularity$Popularity)

CC <- (CityPopularity,
       xvar='City', yvar=c('Mean', 'Popularity'),
       options=list(seriesType='bars',
                    width=450, height=300,
                    title='City Popularity',
                    series='{0: {type:\"line\"}}'))

plot(CC)

```

#### Pros
* Well-developed Google chart library

#### Cons
* displays in browser, not R plot window
* doesn't directly integrate with R Markdown HTML docs - fidgetly to get it to work

## Conclusion

* ggplot for exploration within R and for static charts in R markdown
* get up to speed with more ggvis, as it is likely future of R graphics
* get up to speed on shiny + ggvis
* keep plotly in mind for situations that may arise
