---
title: "Plot Tests"
author: "John Yuill"
date: "December 11, 2016"
output: html_document
---

## PURPOSE
* compare major graphing options

```{r, include=FALSE}
## set global options
knitr::opts_chunk$set(
  echo=FALSE,
  error=FALSE,
  message=FALSE,
  warning=FALSE
)
library(dplyr)

```

* Load required libraries

```{r, echo=TRUE}
library(plotly)
library(ggplot2)
library(ggvis)
library(googleVis)

```

## EXAMPLES

### 1. ggplot2

```{r, echo=FALSE}
ggplot(mtcars, aes(x=disp,y=mpg))+geom_point()

```

#### Pros

* super-control over plot features and format
* uses grammar of graphics
* lots of usage and support
* good skill level already attained, with lots of home-made examples

#### Cons

* no further 'official' development - basically abandoned in favour of ggvis
* no built-in interactivity
* can be cumbersome code
* can't easily download

#### Use

* static charts, including R Markdown HTML files
* maybe with Shiny, but probably choose alternatives below

### 2. ggvis

```{r}
ggvis(mtcars, x = ~disp, y = ~mpg)

```

#### Pros

* designed for more interactivity than ggplot2 (although require shiny)
* defaults to cleaner style than ggplot2
* takes advantage of pipe (%>%) and integrates with dplyr
* easy export/download

#### Cons

* interactivity requires Shiny

#### Use

* in shiny apps

### 3. Plotly

```{r}
plot_ly(mtcars, x = ~disp, y = ~mpg)

```

#### Pros

* full-on library of interactive charts
* can embed charts with some interactivity in R Markdown HTML files

#### Cons

* interactivity is limited to zooming, hover labels (which is cool but not sufficient)
* for shiny, requires library on shiny server - compatible version
* recent update (v4.0) not backwards compatible, breaking older charts

#### Use

* embed in R Markdown HTML for limited interactivity
* possibly with shiny

## 4. Google Viz

```{r setOptions, message=FALSE}
op <- options(gvis.plot.tag='chart')
```

```{r results='asis'}
mtdm <- mtcars %>% select(disp,mpg)
scatter <- gvisScatterChart(mtdm,
                            options=list(
                              pointSize=2,
                              width=400,
                              height=400,
                              legend="none"
                   
                 )
                 )
plot(scatter)
#print(scatter, 'chart')
```

#### Pros
* Well-developed Google chart library

#### Cons
* displays in browser, not R plot window
* doesn't directly integrate with R Markdown HTML docs - fidgetly to get it to work

## Conclusion

* ggplot for exploration within R and for static charts in R markdown
* get up to speed with more ggvis, as it is likely future of R graphics
* get up to speed on shiny + ggvis
* keep plotly in mind for situations that may arise
