---
title: "Gvis test"
author: "John Yuill"
date: "December 11, 2016"
output: html_document
---

* Example taken directly from <https://cran.r-project.org/web/packages/googleVis/vignettes/Using_googleVis_with_knitr.html>
* Charts can be previewed by running code (not full Markdown) in R studio 
* For R Markdown, need to view in BROWSER

```{r setOptions, message=FALSE, cache=FALSE }
library(googleVis)
op <- options(gvis.plot.tag='chart')
```

## Simple example - same as used in 'graphics-options' file
```{r scatterexample, results='asis', echo=FALSE, comments=NA}

mtdm2 <- mtcars[,c(1,3)]
scatter <- gvisScatterChart(mtdm2,
                            options=list(
                              pointSize=2,
                              width=400,
                              height=400,
                              legend="none"
                   
                 )
                 )
plot(scatter) # works in browser but not markdown :(

```

***
### Online examples from link above...

The following plot statements will automatically return  the HTML
required for the 'knitted' output. 

## Combo chart
```{r ComboExample, results='asis', tidy=FALSE, echo=FALSE, cache=TRUE, comment=NA}
## Add the mean
CityPopularity$Mean=mean(CityPopularity$Popularity)
CC <- gvisComboChart(CityPopularity, xvar='City',
          yvar=c('Mean', 'Popularity'),
          options=list(seriesType='bars',
                       width=450, height=300,
                       title='City Popularity',
                       series='{0: {type:\"line\"}}'))
plot(CC) # works in browser; supposed to work in Markdown, accordingly to examples, but doesn't
#CC # doesn't work
#print(CC) # doesn't work
```
Example of gvisComboChart with R code shown above. (If no chart visible: doesn't work)

## Place two charts next to each other
```{r gvisMergeExample, results='asis', echo=FALSE}
Geo <- gvisGeoChart(Exports, locationvar='Country', colorvar='Profit', 
                    options=list(height=300, width=350)) 
Tbl <- gvisTable(Exports, options=list(height=300, width=200))
plot(gvisMerge(Geo, Tbl, horizontal=TRUE))
```

Example of a gvisGeoChart with gvisTable and R code hidden. (If no chart visible: doesn't work)


```{r resetOptions, echo=FALSE}
## Set options back to original options
options(op)
```